---
title: "Take Home_Ex02"
author: "Dabbie Neo"
date: 6/4/2023
date-modified: "`r Sys.Date()`"
execute: 
  echo: true
  eval: true
  warning: false
---

# 1. Background

The country of Oceanus has sought FishEye International's help in identifying companies possibly engaged in illegal, unreported, and unregulated (IUU) fishing. As part of the collaboration, FishEye's analysts received import/export data for Oceanus' marine and fishing industries.

With reference to [Mini-Challenge 2](https://vast-challenge.github.io/2023/MC2.html) of [VAST Challenge 2023](https://vast-challenge.github.io/2023/) and by using appropriate static and interactive statistical graphics methods, we will be helping FishEye to identify companies that may be engaged in illegal fishing.

# 2. Data Source

The data is taken from the [Mini-Challenge 2](https://vast-challenge.github.io/2023/MC2.html) of [VAST Challenge 2023](https://vast-challenge.github.io/2023/). mc2_challenge_graph.json file will be used for the purpose of this exercise.

# 3. Data Preparation

## 3.1 Install and launching R packages

The code chunk below uses p_load() of pacman package to check if packages are installed in the computer. If they are, then they will be launched into R. The R packages installed are:

```{r}
pacman::p_load(jsonlite,tidygraph,ggraph,visNetwork,tidyverse,lubridate,igraph,plotly,treemap)
```

## 3.2 Loading the Data

`fromJSON()` of jsonlite package is used to import mc2_challenge_graph.json into R environment.

```{r}
MC2 <- fromJSON("data/mc2_challenge_graph.json")
```

## 3.3 Data Wrangling

### 3.3.1 Extracting the nodes

The code chunk is used to extract nodes data table from mc2_data list object and save the output in a tibble data frame object called mc2_nodes.

```{r}
#Extract id, shpcountry and rcvcountry and make it as a tibble database. use select to choose the fields you want and reorganise the fields as you want
MC2_nodes <- as_tibble(MC2$nodes) %>%
  select(id, shpcountry, rcvcountry)
head(MC2_nodes)
```

::: callout-note
## Things to learn

`select()` is used not only to select the field needed but also to re-organise the sequence of the fields.
:::

### 3.3.2 Extracting the edges

The code chunk is used to extract edges data table from mc2_data list object and save the output in a tibble data frame object called mc2_edges.

```{r}
MC2_edges <- as_tibble(MC2$links) %>%
  select(source, target, arrivaldate, hscode, valueofgoods_omu, valueofgoodsusd, volumeteu, weightkg)

```

### 3.3.3 Reviewing the imported data

Next, we will examine the structure of the data frame using `glimpse()` of dplyr.

```{r}
glimpse(MC2_nodes)
glimpse(MC2_edges)
```

::: callout-note
## Warning

The output report of MC2_edges above reveals that the arrivaldate is treated as <chr> data type instead of date data type. This is an error! Before we continue, it is important for us to change the data type of arrivaldate field to "Date"" data type.
:::

### 3.3.4 Wrangling Time

```{r}
MC2_edges <- MC2_edges %>%
  mutate(ArrivalDate = ymd(arrivaldate)) %>%
  mutate(Year = year(ArrivalDate)) %>%
  mutate(Month = month(ArrivalDate)) %>%
  mutate(Monthyear = paste(Year, Month, sep = "-")) %>%
  select(source, target, ArrivalDate, Month, Year, hscode, valueofgoods_omu, volumeteu, weightkg, valueofgoodsusd) %>%
  distinct()
head(MC2_edges)
```

::: callout-note
## Things to learn

-   `mutate()` is used 4 times to create 4 derive fields.

    -   `ymd()` of **lubridate** package is used to covert *arrivaldate* field from character data type into date data type.

    -   `year()` of **lubridate** package is used to convert the values in ArrivalDate field into year values.

    -   month() of l**ubridate** package is used to convert the values in ArrivalDate field into month values.

-   `select()` is used not only to select the field needed but also to re-organise the sequent of the fields.
:::

### 3.3.5 Checking if there is any missing values in the edge data table

The below chunck is used to calculate the percentage of NAs and 0s in the each column in the edge data table to see if we should use it for our analysis.

```{r}
# Select specific columns in your dataset
selected_columns <- c("valueofgoods_omu", "volumeteu", "weightkg", "valueofgoodsusd")

## Calculate the percentage of NA values and zeros for the selected columns
total_rows <- nrow(MC2_edges)
na_percentage <- colSums(is.na(MC2_edges[, selected_columns])) / total_rows * 100
zero_percentage <- colSums(MC2_edges[, selected_columns] == 0, na.rm = TRUE) / total_rows * 100

# Combine the results into a data frame
result <- data.frame(NA_Percentage = na_percentage, Zero_Percentage = zero_percentage)

# Display the result
result
```

::: callout-note
## Warning

There is a high percentage of NA value in valueofgoods_omu and valueofgoodusd and a high percentage of zero in volumeteu, thus we will leave them out in our analysis, since we are unable to derive any useful insights.
:::

### 3.3.6 Preparing the edges data table

Harmonized System (HS) codes are the identification codes given to goods for use in international trade. The HS codes are administered by the World Customs Organization (WCO) and are internationally accepted for use by customs authorities and companies to identify goods.

Since we are doing an analysis on the fishing industry, we have to first filter those hscodes that are fishing industry related products.

```{r}
mc2_edges_aggregated <- MC2_edges %>%
  filter(grepl("^30[1-8]|^2301|^160[4-5]|^1212|^1302|^1504|^151610|^151790", hscode)) %>% # filter out only those hscode that are fishing industry related products 
  group_by(source, target, hscode, Year) %>%
    summarise(weights = n(), median_weight = median(weightkg)) %>%
  filter(source!=target) %>%
  filter(weights>10) %>%
  ungroup()
mc2_edges_aggregated
```

Next, we take a look at what are the top fishing related products that has most transactions.

```{r}
top_3_hscode <- mc2_edges_aggregated %>%
  group_by(hscode) %>%
  summarise(total_weights = sum(weights)) %>%
  arrange(desc(total_weights)) %>%
  slice_head(n = 3)

top_3_hscode

```

The top 3 hscodes that has most number of transactions are '306170','304620' and '160414'. Thus, we will focus our analysis based on these 3 hscodes.

```{r}
#Filter the mc2_edges_aggregated based on the top 3 hscode
mc2_edges_aggregated_top <- mc2_edges_aggregated %>%
  filter(hscode == "306170"| hscode == "304620"| hscode == "160414")

#mc2_edges_aggregated_top
```

::: callout-note
## Things to learn

-   `filter()` is used to select records whereby hscode that fishing industry related products. The selection of hscode is referenced from the link [here](https://www.cybex.in/hs-codes/fish-crustaceans-molluscs-aquatic-invertebrates-chapter-03.aspx)

-   `group_by()` is used to aggregate values by source, target, hscode, Year.

-   `summarise()` and `n()` are used to count the aggregated records.

-   filter() is then used to perform the below selection,

    -   to select all records whereby source are not equal to target
:::

### 3.3.7 Preparing the nodes data table

Instead of using the nodes data table extracted from mc2_data, we will prepare a new nodes data table by using the source and target fields of mc2_edges_aggregated data table. This is necessary to ensure that the nodes in nodes data tables include all the source and target values. Then we will reference to the MC2_nodes table to get the corresponding shpcountry and rcvcountry values.

```{r}
id1_aggregated <- mc2_edges_aggregated_top %>%
  select(source) %>%
  rename(id = source)
id2_aggregated <- mc2_edges_aggregated_top %>%
  select(target) %>%
  rename(id = target)
mc2_nodes_extracted_aggregated <- rbind(id1_aggregated, id2_aggregated) %>%
  distinct()

# Join with MC2_nodes by 'id to get the 'shpcountry', and 'rcvcountry'
mc2_nodes_extracted_aggregated <- mc2_nodes_extracted_aggregated %>%
  left_join(MC2_nodes, by = "id")
head(mc2_nodes_extracted_aggregated)
```

### 3.3.8 Building the tidygraph model

The code chunk below is then used to build the tidy graph data model.

```{r}
mc2_graph <- tbl_graph(nodes = mc2_nodes_extracted_aggregated,
                       edges = mc2_edges_aggregated_top,
                       directed = TRUE)
mc2_graph
```

# 4. Network Metrics Analysis

## 4.1 Calculating the in, out and total degree centrality of the nodes

`Degree centrality` is a measure of immediate connection in a network. It could be interpreted as immediate reach in a social network.`Eigenvector centrality` is a measure that takes into account both the number of connections that a node or an actor has, and the degree of influence that the node's immediate connections have in the entire network.

We will calculate the in, out and total degree centrality of the nodes, and use `mutate()` to create new columns to store these values.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 4
#| fig-width: 4

#| echo: false
#| fig-width: 3
#| fig-height: 3

# Calulate the in, out and total degree centrality and add 3 new columns via mutate() to store the values 
mc2_graph <- mc2_graph %>%
  activate(nodes) %>%
  mutate(
    in_degree_centrality = centrality_degree(mode = "in"),
    out_degree_centrality = centrality_degree(mode = "out"),
    degree_centrality = centrality_degree(mode = "all"),
    eigen_centrality = centrality_eigen()
  ) %>%
  mutate(combined_centrality = degree_centrality * eigen_centrality) %>%
  arrange(desc(combined_centrality)) 
mc2_graph

```
Below code chunk to find out the top 20 id that has a high combined degree and eigenvector centrality score. 

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 4
#| fig-width: 4

#| echo: false
#| fig-width: 3
#| fig-height: 3

#Select the top 20 IDs based on centrality value
top_20_ids <- mc2_graph %>%
  activate(nodes) %>%
  as_tibble() %>%
  pull(id) %>%
  head(20)

top_20_ids

```

Bsed on the table above, we can see that the top 20 actors with high combined degree and eigen centrality value, include Mar del Este CJSC, Caracola del Sol Services and hǎi dǎn Corporation Wharf.

::: callout-note
## Things to learn

`activate()` is used to make the nodes of mc2_graph active to calculate the degree centrality.

`mutate()` function from the dplyr package is used to add two new columns, in_degree_centrality and out_degree_centrality, to the nodes of the mc2_graph object
:::

## 4.2 Determining the type of entity the id belongs to

```{r}
#Specify what entity the id could be 
mc2_graph <- mc2_graph %>%
  mutate(
    node_type = case_when(
      in_degree_centrality == 0 & out_degree_centrality > 0 ~ "vessels",
      in_degree_centrality > 0 & out_degree_centrality == 0 ~ "transshipment",
      in_degree_centrality > 0 & out_degree_centrality > 0 ~ "vessels/transshipment"
    )
  )

```

### 4.2.1 Counting number of entities for each business type

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 4
#| fig-width: 4

#| echo: false
#| fig-width: 3
#| fig-height: 3

#Count the how many id belong to each entity
vessels_count <- mc2_graph %>%
  activate(nodes) %>%
  as_tibble() %>%
  filter(node_type == "vessels") %>%
  nrow()

transhipment_count <- mc2_graph %>%
  activate(nodes) %>%
  as_tibble() %>%
  filter(node_type == "transshipment") %>%
  nrow()

both_count <- mc2_graph %>%
  activate(nodes) %>%
  as_tibble() %>%
  filter(node_type == "vessels/transshipment") %>%
  nrow()

# cat("Number of vessels:", vessels_count, "\n")
# cat("Number of transshipment:", transhipment_count, "\n")
# cat("Number of vessels/transshipment:", both_count, "\n")

```

After cleaning up the data, we have a total of 529 vessels, 388 transshipment and 13 companies that may be either a vessel or transshipment to work with for our analysis.

::: callout-note
## Note

-   If in_degree_centrality == 0, it means that the company is most likely a pure exporter and highly likely a vessel.

-   If out_degree_centrality == 0, it means that the company is most likely a pure importer and highly likely involved in transshipment.

-   If in_degree_centrality \> 0 & out_degree_centrality \> 0, the company is most likely both a vessel or transshipment.
:::

## 4.3 Visualising the network graph with ggraph

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 5
#| fig-width: 8

#| echo: false
#| fig-width: 3
#| fig-height: 3

ggraph(mc2_graph,
       layout = "fr") +
  geom_edge_link(aes(width=weights), 
                 alpha=0.2) +
  geom_node_point(aes(colour = node_type)) +
  theme_graph() +
  labs(title = "Network graph of global transhipment activities")

```

## 4.4 Flag Based Network

To gain a better understanding of the prevalence of the types of flags in the transshipment events, we can find out which country the vessels tends to be most often associated with when shipping.

And we can see that vessels tend to ship to Merigrad and Marebak.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 4
#| fig-width: 4

#| echo: false
#| fig-width: 3
#| fig-height: 3

country_id_counts_shp <- mc2_graph %>%
  activate(nodes) %>%
  as_tibble() %>%
  filter(in_degree_centrality == 0) %>% # filter out for the vessels 
  group_by(shpcountry) %>%
  summarise(id_count = n_distinct(id)) %>%
  arrange(desc(id_count))

head(country_id_counts_shp)

```

Also, we can see that for transshipment, companies are most often associated with Oceanus when receiving their products.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 5
#| fig-width: 8

#| echo: false
#| fig-width: 3
#| fig-height: 3

country_id_counts_rcv <- mc2_graph %>%
  activate(nodes) %>%
  as_tibble() %>%
  filter(out_degree_centrality == 0) %>% # filter out for the vessels 
  group_by(rcvcountry) %>%
  summarise(id_count = n_distinct(id)) %>%
  arrange(desc(id_count))

head(country_id_counts_rcv)
```

## 4.5 Top 20 transshipment companies trading frequencies

Check out the trading frequencies of the top 20 transshipment companies trading frequencies over the years. These top 20 companies are those who has high in-degree centrality.

We can see that the total transactions fluctuates more for Caracola del Sol Services, Mar del Este CJSC and Pao gan SE Seal.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 5
#| fig-width: 8

#| echo: false
#| fig-width: 3
#| fig-height: 3

#Select the top 20 IDs based on centrality value
top_20_ids <- mc2_graph %>%
  activate(nodes) %>%
  as_tibble() %>%
  arrange(desc(in_degree_centrality)) %>%
  pull(id) %>%
  head(20)

# Filter the mc2_edges_aggregated_top dataframe
filtered_edges_entities <- mc2_edges_aggregated_top %>%
  filter(target %in% top_20_ids) %>%
  group_by(Year, target) %>%
  summarise(total_weight = sum(weights))

# Plot the aggregated weights
p <- ggplot(filtered_edges_entities, aes(x = Year, y = total_weight, color = target)) +
  geom_line() +
  geom_point() +
  labs(x = "Year", y = "Total transactions", title = "Number of Transactions by Year") +
  scale_color_discrete(name = "Target Entity")

ggplotly(p)
```

## 4.6 Community Detection Analysis

Next, we will do a community detection analysis using the `group_edge_betweenness` function. It works by iteratively removing the edges with the highest betweenness centrality, which is a measure of the number of shortest paths that pass through an edge. By removing these edges, the graph is divided into clusters or communities.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 5
#| fig-width: 8

#| echo: false
#| fig-width: 3
#| fig-height: 3

set.seed(123)
mc2_graph <- mc2_graph %>%
   mutate(community = as.factor(group_edge_betweenness(weights = weights, directed = TRUE)))

g_mcgraph <- mc2_graph %>%
  activate(nodes) %>%
  group_by(community) %>%
  filter(n() > 2) %>%    #filter the community size > 2
  ungroup() %>%
  ggraph(layout = "fr") + 
  geom_edge_link(aes(width = weights), 
                 alpha = 0.2,
                 arrows = "to") +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = community)) +
  theme_graph()

g_mcgraph
```

As seen from the community detection graph above, after filtering for community size \> 2, there are 9 community shown, and looking at the connectivity and density of the graph, it seems that community 1, seems to be the most densely populated. Thus, for the following analysis, we shall focus on community 1.

The code chunk below can be used to find out which node has the highest in-degree centrality for in community 1. And we can see that within community 1, Mar del Este CJSC has the highest in-degree centrality score.

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 5
#| fig-width: 8

#| echo: false
#| fig-width: 3
#| fig-height: 3

indegree_community <- mc2_graph %>%
  activate(nodes) %>%
  filter(community == 1) %>%
  mutate(in_degree_centrality_community = centrality_degree(mode = "in")) %>%
  arrange(desc(in_degree_centrality_community)) %>%
  as_tibble()

head(indegree_community, 5)
```

## 4.7 Plotting the visNetwork graph of transshipment leader 

Next, we will further investigate our highest transshipment node, `Mar del Este CJSC`, by plotting its network graph over the years from 2028-2034 to see if we can find any insights.

Looking at the network graph below, we can see that initially in 2028, Marine Mates NV Worldwide and ReefRider Foods Lte Corporation Family supplies goods to Mar del Este CSJC but disappears in 2029. And in 2032, there are 2 new suppliers, The Salty Dog Limited Liability Company and Turkish Salmon A/S Marine, however, both disappeared in 2034. 


```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 6
#| fig-width: 9

#| echo: false
#| fig-width: 3
#| fig-height: 3

# Filter the year and id in edges and the corresponding id
filtered_graph_2028 <- mc2_graph %>%
  activate(edges) %>%
  filter(Year == 2028, to == 1)

unique_ids_2028 <- unique(c(filtered_graph_2028 %>%
                         activate(edges) %>%
                         pull(from),
                       filtered_graph_2028 %>%
                         activate(edges) %>%
                         pull(to)))

filtered_graph_2028 <- filtered_graph_2028 %>%
  activate(nodes) %>%
  filter(row_number() %in% unique_ids_2028) %>%
  as_tbl_graph()

edges_df_2028 <- filtered_graph_2028 %>%
  activate(edges) %>%
  as_tibble()

nodes_df_2028 <- filtered_graph_2028 %>%
  activate(nodes) %>%
  as_tibble() %>%
  rename(label = id) %>%
  mutate(id=row_number()) %>%
  select(everything()) %>%
  relocate(id, .before = label)

nodes_df_2028<- nodes_df_2028 %>%
  rename(group = node_type) 

# Plot the network graph with labeled nodes using visNetwork
vis_2028 <- visNetwork(nodes_df_2028, edges_df_2028, submain = list(text = "Network Graph of Mar del Este CJSC in 2028 ",
                          style = "font-family:Comic Sans MS;color:#000000;font-size:15px;text-align:center;")) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(arrows = "to") %>%
  visOptions(
    highlightNearest = TRUE,
    nodesIdSelection = TRUE,
  ) %>%
  visLegend() %>%
  visInteraction(zoomView = TRUE, dragNodes = TRUE, dragView = TRUE, navigationButtons = TRUE)
vis_2028
```

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 6
#| fig-width: 9

#| echo: false
#| fig-width: 3
#| fig-height: 3

# Filter the year and id in edges and the corresponding id
filtered_graph_2029 <- mc2_graph %>%
  activate(edges) %>%
  filter(Year == 2029, to == 1)

unique_ids_2029 <- unique(c(filtered_graph_2029 %>%
                         activate(edges) %>%
                         pull(from),
                       filtered_graph_2029 %>%
                         activate(edges) %>%
                         pull(to)))

filtered_graph_2029 <- filtered_graph_2029 %>%
  activate(nodes) %>%
  filter(row_number() %in% unique_ids_2029) %>%
  as_tbl_graph()

edges_df_2029 <- filtered_graph_2029 %>%
  activate(edges) %>%
  as_tibble()

nodes_df_2029 <- filtered_graph_2029 %>%
  activate(nodes) %>%
  as_tibble() %>%
  rename(label = id) %>%
  mutate(id=row_number()) %>%
  select(everything()) %>%
  relocate(id, .before = label)

nodes_df_2029<- nodes_df_2029 %>%
  rename(group = node_type) 

# Plot the network graph with labeled nodes using visNetwork
vis_2029 <- visNetwork(nodes_df_2029, edges_df_2029, submain = list(text = "Network Graph of Mar del Este CJSC in 2029 ",
                          style = "font-family:Comic Sans MS;color:#000000;font-size:15px;text-align:center;")) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(arrows = "to") %>%
  visOptions(
    highlightNearest = TRUE,
    nodesIdSelection = TRUE,
  ) %>%
  visLegend() %>%
  visInteraction(zoomView = TRUE, dragNodes = TRUE, dragView = TRUE, navigationButtons = TRUE)
vis_2029

```

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 6
#| fig-width: 9

#| echo: false
#| fig-width: 3
#| fig-height: 3

filtered_graph_2030 <- mc2_graph %>%
  activate(edges) %>%
  filter(Year == 2030, to == 1)

unique_ids_2030 <- unique(c(filtered_graph_2030 %>%
                         activate(edges) %>%
                         pull(from),
                       filtered_graph_2030 %>%
                         activate(edges) %>%
                         pull(to)))

filtered_graph_2030 <- filtered_graph_2030 %>%
  activate(nodes) %>%
  filter(row_number() %in% unique_ids_2030) %>%
  as_tbl_graph()

edges_df_2030 <- filtered_graph_2030 %>%
  activate(edges) %>%
  as_tibble()

nodes_df_2030 <- filtered_graph_2030 %>%
  activate(nodes) %>%
  as_tibble() %>%
  rename(label = id) %>%
  mutate(id=row_number()) %>%
  select(everything()) %>%
  relocate(id, .before = label)

nodes_df_2030<- nodes_df_2030 %>%
  rename(group = node_type) 

# Plot the network graph with labeled nodes using visNetwork
vis_2030 <- visNetwork(nodes_df_2030, edges_df_2030, submain = list(text = "Network Graph ofMar del Este CJSC in 2030 ",
                          style = "font-family:Comic Sans MS;color:#000000;font-size:15px;text-align:center;")) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(arrows = "to") %>%
  visOptions(
    highlightNearest = TRUE,
    nodesIdSelection = TRUE,
  ) %>%
  visLegend() %>%
  visInteraction(zoomView = TRUE, dragNodes = TRUE, dragView = TRUE, navigationButtons = TRUE) 
vis_2030

```

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 6
#| fig-width: 9

#| echo: false
#| fig-width: 3
#| fig-height: 3

filtered_graph_2031 <- mc2_graph %>%
  activate(edges) %>%
  filter(Year == 2031, to == 1)

unique_ids_2031 <- unique(c(filtered_graph_2031 %>%
                         activate(edges) %>%
                         pull(from),
                       filtered_graph_2031 %>%
                         activate(edges) %>%
                         pull(to)))

filtered_graph_2031 <- filtered_graph_2031 %>%
  activate(nodes) %>%
  filter(row_number() %in% unique_ids_2031) %>%
  as_tbl_graph()

edges_df_2031 <- filtered_graph_2031 %>%
  activate(edges) %>%
  as_tibble()

nodes_df_2031 <- filtered_graph_2031 %>%
  activate(nodes) %>%
  as_tibble() %>%
  rename(label = id) %>%
  mutate(id=row_number()) %>%
  select(everything()) %>%
  relocate(id, .before = label)

nodes_df_2031<- nodes_df_2031 %>%
  rename(group = node_type) 

# Plot the network graph with labeled nodes using visNetwork
vis_2031 <- visNetwork(nodes_df_2031, edges_df_2031, submain = list(text = "Network Graph ofMar del Este CJSC in 2031 ",
                          style = "font-family:Comic Sans MS;color:#000000;font-size:15px;text-align:center;")) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(arrows = "to") %>%
  visOptions(
    highlightNearest = TRUE,
    nodesIdSelection = TRUE,
  ) %>%
  visLegend() %>%
  visInteraction(zoomView = TRUE, dragNodes = TRUE, dragView = TRUE, navigationButtons = TRUE) 
vis_2031
```

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 6
#| fig-width: 9

#| echo: false
#| fig-width: 3
#| fig-height: 3

filtered_graph_2032 <- mc2_graph %>%
  activate(edges) %>%
  filter(Year == 2032, to == 1)

unique_ids_2032 <- unique(c(filtered_graph_2032 %>%
                         activate(edges) %>%
                         pull(from),
                       filtered_graph_2032 %>%
                         activate(edges) %>%
                         pull(to)))

filtered_graph_2032 <- filtered_graph_2032 %>%
  activate(nodes) %>%
  filter(row_number() %in% unique_ids_2032) %>%
  as_tbl_graph()

edges_df_2032 <- filtered_graph_2032 %>%
  activate(edges) %>%
  as_tibble()

nodes_df_2032 <- filtered_graph_2032 %>%
  activate(nodes) %>%
  as_tibble() %>%
  rename(label = id) %>%
  mutate(id=row_number()) %>%
  select(everything()) %>%
  relocate(id, .before = label)

nodes_df_2032<- nodes_df_2032 %>%
  rename(group = node_type) 

# Plot the network graph with labeled nodes using visNetwork
vis_2032 <- visNetwork(nodes_df_2032, edges_df_2032, submain = list(text = "Network Graph ofMar del Este CJSC in 2032 ",
                          style = "font-family:Comic Sans MS;color:#000000;font-size:15px;text-align:center;")) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(arrows = "to") %>%
  visOptions(
    highlightNearest = TRUE,
    nodesIdSelection = TRUE,
  ) %>%
  visLegend() %>%
  visInteraction(zoomView = TRUE, dragNodes = TRUE, dragView = TRUE, navigationButtons = TRUE) 
vis_2032
```

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 6
#| fig-width: 9

#| echo: false
#| fig-width: 3
#| fig-height: 3

filtered_graph_2033 <- mc2_graph %>%
  activate(edges) %>%
  filter(Year == 2033, to == 1)

unique_ids_2033 <- unique(c(filtered_graph_2033 %>%
                         activate(edges) %>%
                         pull(from),
                       filtered_graph_2033 %>%
                         activate(edges) %>%
                         pull(to)))

filtered_graph_2033 <- filtered_graph_2033 %>%
  activate(nodes) %>%
  filter(row_number() %in% unique_ids_2033) %>%
  as_tbl_graph()

edges_df_2033 <- filtered_graph_2033 %>%
  activate(edges) %>%
  as_tibble()

nodes_df_2033 <- filtered_graph_2033 %>%
  activate(nodes) %>%
  as_tibble() %>%
  rename(label = id) %>%
  mutate(id=row_number()) %>%
  select(everything()) %>%
  relocate(id, .before = label)

nodes_df_2033<- nodes_df_2033 %>%
  rename(group = node_type) 

# Plot the network graph with labeled nodes using visNetwork
vis_2033 <- visNetwork(nodes_df_2033, edges_df_2033, submain = list(text = "Network Graph ofMar del Este CJSC in 2033 ",
                          style = "font-family:Comic Sans MS;color:#000000;font-size:15px;text-align:center;")) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(arrows = "to") %>%
  visOptions(
    highlightNearest = TRUE,
    nodesIdSelection = TRUE,
  ) %>%
  visLegend() %>%
  visInteraction(zoomView = TRUE, dragNodes = TRUE, dragView = TRUE, navigationButtons = TRUE) 
vis_2033
```

```{r}
#| code-fold: true
#| code-summary: "Show the code"
#| fig-height: 6
#| fig-width: 9

#| echo: false
#| fig-width: 3
#| fig-height: 3

filtered_graph_2034 <- mc2_graph %>%
  activate(edges) %>%
  filter(Year == 2034, to == 1)

unique_ids_2034 <- unique(c(filtered_graph_2034 %>%
                         activate(edges) %>%
                         pull(from),
                       filtered_graph_2034 %>%
                         activate(edges) %>%
                         pull(to)))

filtered_graph_2034 <- filtered_graph_2034 %>%
  activate(nodes) %>%
  filter(row_number() %in% unique_ids_2034) %>%
  as_tbl_graph()

edges_df_2034 <- filtered_graph_2034 %>%
  activate(edges) %>%
  as_tibble()

nodes_df_2034 <- filtered_graph_2034 %>%
  activate(nodes) %>%
  as_tibble() %>%
  rename(label = id) %>%
  mutate(id=row_number()) %>%
  select(everything()) %>%
  relocate(id, .before = label)

nodes_df_2034<- nodes_df_2034 %>%
  rename(group = node_type) 

# Plot the network graph with labeled nodes using visNetwork
vis_2034 <- visNetwork(nodes_df_2034, edges_df_2034, submain = list(text = "Network Graph ofMar del Este CJSC in 2034 ",
                          style = "font-family:Comic Sans MS;color:#000000;font-size:15px;text-align:center;")) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(arrows = "to") %>%
  visOptions(
    highlightNearest = TRUE,
    nodesIdSelection = TRUE,
  ) %>%
  visLegend() %>%
  visInteraction(zoomView = TRUE, dragNodes = TRUE, dragView = TRUE, navigationButtons = TRUE) 
vis_2034
```

# 5. References

A. Petrossian,G., Barthuly,B.,C. Sosnowski,M.(2022).Identifying Central Carriers and Detecting Key Communities Within the Global Fish Transshipment Networks. Retrieved June 4, 2032, from <https://www.frontiersin.org/articles/10.3389/fmars.2022.798893/full>

J. Park,A.,Z. Stamato,S.(2020).Social Network Analysis of Global Transshipment: A Framework for Discovering Illegal Fishing.

Datastorm(nd).visNetowork,an R package for an interactive network visualistion. Retrieved June 4, 2032, from <https://datastorm-open.github.io/visNetwork/edges.html>

[https://tidygraph.data-imaginist.com/index.html https://ona-book.org/vertex-importance.html](https://tidygraph.data-imaginist.com/index.html https://ona-book.org/vertex-importance.html)
[6 Vertex Importance and Centrality \| Handbook of Graphs and Networks in People Analytics (ona-book.org)](https://ona-book.org/vertex-importance.html)


