---
title: "Take Home_Ex03"
author: "Dabbie Neo"
date: 6/3/2023
date-modified: "`r Sys.Date()`"
execute: 
  echo: true
  eval: true
  warning: false
---

# 1. Background

The country of Oceanus has sought FishEye International's help in identifying companies possibly engaged in illegal, unreported, and unregulated (IUU) fishing. As part of the collaboration, FishEye's analysts received import/export data for Oceanus' marine and fishing industries.

With reference to [Mini-Challenge 3](https://vast-challenge.github.io/2023/MC3.html) of [VAST Challenge 2023](https://vast-challenge.github.io/2023/) and by using appropriate static and interactive statistical graphics methods, we will be helping FishEye to identify companies that may be engaged in illegal fishing.

# 2. Data Source

The data is taken from the [Mini-Challenge 3](https://vast-challenge.github.io/2023/MC3.html) of [VAST Challenge 2023](https://vast-challenge.github.io/2023/). 

# 3. Data Preparation

## 3.1 Install and launching R packages

The code chunk below uses p_load() of pacman package to check if packages are installed in the computer. If they are, then they will be launched into R. The R packages installed are:

```{r}
pacman::p_load(jsonlite,tidygraph,ggraph,visNetwork,tidyverse,graphlayouts, ggforce, tidytext)
```

## 3.2 Loading the Data

`fromJSON()` of jsonlite package is used to import MC3.json into R environment.

```{r}
Mc3_data <- fromJSON("data/MC3.json")
```

```{r}
mc3_edges <- as_tibble(Mc3_data$links)

```

```{r}
mc3_edges <- as_tibble(Mc3_data$links) %>%
  distinct() %>%
  mutate(source = as.character(source),
         target = as.character(target),
         type = as.character(type)) %>%
  group_by(source, target, type) %>%
  summarise(weights = n()) %>%
  filter(source != target) %>%
  ungroup()

```
```{r}
mc3_nodes <- as_tibble(Mc3_data$nodes) %>%
  mutate(country = as.character(country),
         id = as.character(id),
         product_services = as.character(product_services),
         revenue_omu = as.numeric(as.character(revenue_omu)),
         type = as.character(type)) %>%
  select(id, country, type, revenue_omu, product_services) #select() used to organise the sequence of col 

```


## 3.3 Data Wrangling

```{r}


```



