---
title: "In-Class Exercise 4"
author: "Dabbie Neo"
date: 5/6/2023
date-modified: "`r Sys.Date()`"
execute: 
  echo: true
  eval: true
  warning: false 
---

# 1. Getting Started

## Install and launching R packages

```{r}
pacman::p_load(rstatix,gt,patchwork,tidyverse,ggstatsplot,ggpubr)
```

## Importing data

```{r}
exam_data <- read_csv("data/Exam_data.csv")
```

## 2. Visualising Normal Distribution

## 2.1 Using QQplot

::: panel-tabset
## The plot

```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
ggplot(exam_data,
       aes(sample=ENGLISH))+
  stat_qq() +
  stat_qq_line()
```

## The code chunk

```{r}
#| eval: false
#| fig-width: 4
#| fig-height: 4
ggplot(exam_data,
       aes(sample=ENGLISH))+
  stat_qq() +
  stat_qq_line()
```
:::

::: callout-note
We can see that the points deviate significantly from the straight diagonal line. This is a clear indication that the set of data is not normally distributed.
:::

## 2.1.1 Combining statistical graph and analysis table

::: panel-tabset
## The plot

```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
qq <- ggplot(exam_data,
       aes(sample=ENGLISH))+
  stat_qq() +
  stat_qq_line()

sw_t <- exam_data %>%
  shapiro_test(ENGLISH) %>%
  gt() #make it to gt format to give a nice table

tmp <- tempfile(fileext = '.png')
gtsave(sw_t, tmp)
table_png <- png::readPNG(tmp,native=TRUE) #sw_t cant be recognised by patchwork so change it to png

qq + table_png
```

## The code chunk

```{r}
#| eval: false
#| fig-width: 4
#| fig-height: 4
ggplot(exam_data,
       aes(sample=ENGLISH))+
  stat_qq() +
  stat_qq_line()
```
:::
